NDNS multilevel carb_50, 7 time slots

### 2018-07-30 paper/Chapters/Chapter2.tex
LCGA method adding, 7 slots results updated

The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability. In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.

@@

>>>>

The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability. In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2. \vspace{-0.3cm}

@@

%LCGA is a statistical approach that models patterns in longitudinal data by classifying individuals into unobserved latent classes with more homogeneous patterns. LCGA is a special type of Growth Mixture Models (GMM), in which the variance of latent slope and intercept are fixed to zero within class, and allowed to vary only across classes. LCGA assumes that all individual growth trajectories within classes are homogeneous.

LCGA is a semi‐parametric technique used to identify distinct subgroups of individuals following a similar pattern of change over time on a given variable. The analysis identifies distinct subgroups of individuals following a distinct pattern of change over time.  LCGA is a special type of Growth Mixture Models (GMM), in which the variance of latent slope and intercept are fixed to zero within class, and allowed to vary only across classes. LCGA assumes that all individual growth trajectories within classes are homogeneous.

In the NDNS RP data context, we considered a latent categorical variable $c_i$ representing the unobserved subpopulation membership (latent class variable) for participant $i, (c_i = 1,2,\cdots K)$.

### 2018-07-30 results/Summary of all the analysis and links.Rmd
LCGA method adding, 7 slots results updated

---
title: "Summary of the analyses we have done"
author: "Chaochen Wang"
date: "29 July 2018, Updated at `r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

@@

@@

- Proposed solutions: 
    - 3 by 3 multilevel LCA solutions (Fig 3.1 and 3.3): 
        - **Type 1 days**: **high carb** at breakfast, afternoon snack, and before bedtime snack;
        - **Type 2 days**: low carb through out the day, **high probability of not having breakfast**;
        - **Type 3 days**: high carb breakfast, low carb lunch and dinner, **not eating at night**.
    - Proportions of three types of days in person level classes:
        - **Class 1 persons (28.2%)**:  62.3%, 20.5%, and 17.2%; 
        - **Class 2 persons (28.9%)**:  40.0%, 42.0%, and 18.0%;
        - **Class 3 persons (42.8%)**:  25.8%, 50.0%, and 24.1%.

@@

- Proposed solutions: Fig 4.
    - 3 classes: 
        - Class 1 (67.2%): high carb breakfast, low carb lunch and dinner; 
        - Class 2 (21.9%): high prob of skipping breakfast, not eating at night; 
        - Class 3 (10.9%): high carb all four days, snacking a alot.

>>>>

---
title: "Summary of the analyses we have done"
author: "Chaochen Wang"
date: "29 July 2018 created, `r Sys.Date()` updated"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

@@

### Table 1 for latent classes identified (24 hours)

[Rpubs link:http://rpubs.com/winterwang/NDNStable1](http://rpubs.com/winterwang/NDNStable1)

@@

- Proposed solutions: 
    - 3 by 3 multilevel LCA solutions (Fig 3.1 and 3.3): 
        - **Type 1 days**: **high carb** at breakfast, afternoon snack, and before bedtime snack;
        - **Type 2 days**: low carb through out the day, **high probability of not having breakfast**;
        - **Type 3 days**: high carb breakfast, low carb lunch and dinner, **not eating at night**.
    - Proportions of three types of days in person level classes:
        - **Class 1 persons (28.2%)**:  62.3%, 20.5%, and 17.2%; -> higher BMI, WC, more DM than the other two groups
        - **Class 2 persons (28.9%)**:  40.0%, 42.0%, and 18.0%;
        - **Class 3 persons (42.8%)**:  25.8%, 50.0%, and 24.1%.

@@

- Proposed solutions: Fig 4.
    - 3 classes: 
        - Class 1 (67.2%): high carb breakfast, low carb lunch and dinner; 
        - Class 2 (21.9%): high prob of skipping breakfast, not eating at night; 
        - Class 3 (10.9%): high carb all four days, snacking frequently. -> also high physical activity, high prob in drinking and smoking

### Table 1 for latent classes identified (7 time slots)

[Rpubs link:http://rpubs.com/winterwang/tab1slots7](http://rpubs.com/winterwang/tab1slots7)

### 2018-07-30 results/Summary of survey analysis.Rmd
LCGA method adding, 7 slots results updated

---
title: "Summary of Survey Analysis"
author: "Chaochen Wang"
date: "27 July 2018"
output:
  html_document:
    nature:
      highlightLines: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

>>>>

---
title: "Summary of Survey Analysis NDNS carb50, 24 hours"
author: "Chaochen Wang"
date: "27 July 2018 created, `r Sys.Date()` updated"
output:
  html_document:
    nature:
      highlightLines: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

### 2018-07-30 results/Timeslots/multilevel.Rmd
LCGA method adding, 7 slots results updated

---
title: "NDNS multilevel carb_50, 7 time slots"
author: "Chaochen Wang"
date: "29 July 2018, Updated at `r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

@@

```{r echo=FALSE, fig.height=8, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 1 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
      theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 2 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

@@

```{r echo=FALSE, fig.height=8, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 1 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
      theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 2 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=Slots, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
      theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 3 days", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

>>>>

---
title: "NDNS multilevel carb_50, 7 time slots"
author: "Chaochen Wang"
date: "29 July 2018 created, `r Sys.Date()` updated"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

@@

```{r echo=FALSE, fig.height=6, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)

pp_long$Time <- as.character(pp_long$Slots)
pp_long$Time[pp_long$Slots == "Breakfast"] <- 7.5
pp_long$Time[pp_long$Slots == "Morning.snack"] <- 10.5
pp_long$Time[pp_long$Slots == "Lunch"] <- 13
pp_long$Time[pp_long$Slots == "Afternoon.snack"] <- 15.5
pp_long$Time[pp_long$Slots == "Dinner"] <- 18.5
pp_long$Time[pp_long$Slots == "Before.bedtime.snack"] <- 21
pp_long$Time[pp_long$Slots == "Midnight.food"] <- 26
pp_long$Time <- as.numeric(pp_long$Time)

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo))  + 
  scale_x_continuous(limits = c(6, 29),
  breaks = seq(6, 29, by = 1)) +
  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") +
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 1 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1)) #+ 
  # scale_x_discrete(labels = c("6","7","8","9","10","11","12","13","14",
  #                             "15","16","17","18","19", "20","21","22",
  #                             "23","0","1","2","3","4","5"))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) + 
  scale_x_continuous(limits = c(6, 29),
  breaks = seq(6, 29, by = 1)) +
  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") +
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 2 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

@@

```{r echo=FALSE,fig.height=6, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)

pp_long$Time <- as.character(pp_long$Slots)
pp_long$Time[pp_long$Slots == "Breakfast"] <- 7.5
pp_long$Time[pp_long$Slots == "Morning.snack"] <- 10.5
pp_long$Time[pp_long$Slots == "Lunch"] <- 13
pp_long$Time[pp_long$Slots == "Afternoon.snack"] <- 15.5
pp_long$Time[pp_long$Slots == "Dinner"] <- 18.5
pp_long$Time[pp_long$Slots == "Before.bedtime.snack"] <- 21
pp_long$Time[pp_long$Slots == "Midnight.food"] <- 26
pp_long$Time <- as.numeric(pp_long$Time)

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo))  + 
  scale_x_continuous(limits = c(6, 29),
  breaks = seq(6, 29, by = 1)) +
  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") +
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 1 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1)) #+ 
  # scale_x_discrete(labels = c("6","7","8","9","10","11","12","13","14",
  #                             "15","16","17","18","19", "20","21","22",
  #                             "23","0","1","2","3","4","5"))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) + 
  scale_x_continuous(limits = c(6, 29),
  breaks = seq(6, 29, by = 1)) +
  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") +
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 2 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) + 
  scale_x_continuous(limits = c(6, 29),
  breaks = seq(6, 29, by = 1)) +
  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") +
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 3 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))
